### 2016-05-17 text/ms.Rmd
Add intro paragraph to methods

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [x] add back in the roc plot and sentence in the main text
- [x] rerun the main simulation analysis because the equations of change for the slope
- [ ] manually adjusted the labels in figure 4
- [x] update the magic number get inserted to use the equation that only has the basic model
- [ ] check figure order
- [ ] check all remaining in-text todo items
-->

@@

TODO ADD OVERVIEW HERE.

>>>>

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [x] add back in the roc plot and sentence in the main text
- [x] rerun the main simulation analysis because the equations of change for the slope
- [x] manually adjusted the labels in figure 4
- [x] update the magic number get inserted to use the equation that only has the basic model
- [x] check figure order
- [ ] check all remaining in-text todo items
-->

@@

To test the ability of superensembles to improve estimates of status and trend in data-limited fish stocks, we first fit four individual assessment models to a large simulated dataset of fish stocks. We then built and tested the performance of superensembles using cross-validation of the simulated dataset. Finally, we tested superensembles built with the entire simulated dataset against a database of global fish sticks. We describe these steps in detail below and illustrate the general approach both with illustrations and pseudocode in Fig. 2.
